Robust Adaptation to Multi-Scale Climate Variability

### 2019-08-25 report-earths-future/paper-2018-robust-adaptation-cyclical-risk.tex
use autoenv and fix word issue

% Abstract
\begin{abstract}
  The assessment and implementation of structural or financial instruments for climate risk mitigation requires projections of future climate risk over the operational life of each proposed instrument.
  A point often neglected in the climate adaptation literature is that the physical sources of predictability differ between projects with long and short planning periods: while historical and paleo climate records emphasizemodes of variability, \acrlong{acc} is expected to alter their occurrence at longer time scales.
  In this paper we present a set of stylized experiments to assess the uncertainties and biases involved in estimating future climate risk over a finite future period, given a limited observational record.
  These experiments consider both quasi-periodic and secular change for the underlying risk, as well as statistical models for estimating this risk from an $N$-year historical record.
  The uncertainty of \acrshort{ipcc}-like future scenarios is considered through an equivalent sample size $N$. 
  The relative importance of estimating the short- or long-term risk extremes depends on the investment life $M$.
  Shorter design lives are preferred for situations where inter-annual to decadal variability can be successfully identified and predicted, suggesting the importance of sequential investment strategies for adaptation.
\end{abstract}

>>>>

% Abstract
\begin{abstract}
  The assessment and implementation of structural or financial instruments for climate risk mitigation requires projections of future climate risk over the operational life of each proposed instrument.
  A point often neglected in the climate adaptation literature is that the physical sources of predictability differ between projects with long and short planning periods: while historical and paleo climate records emphasize low-frequency modes of variability, \acrlong{acc} is expected to alter their occurrence at longer time scales.
  In this paper we present a set of stylized experiments to assess the uncertainties and biases involved in estimating future climate risk over a finite future period, given a limited observational record.
  These experiments consider both quasi-periodic and secular change for the underlying risk, as well as statistical models for estimating this risk from an $N$-year historical record.
  The uncertainty of \acrshort{ipcc}-like future scenarios is considered through an equivalent sample size $N$. 
  The relative importance of estimating the short- or long-term risk extremes depends on the investment life $M$.
  Shorter design lives are preferred for situations where inter-annual to decadal variability can be successfully identified and predicted, suggesting the importance of sequential investment strategies for adaptation.
\end{abstract}
